\TheTitle

### 2017-07-15 paper/relatedwork.tex
make use of "Merge-Tree" consistent
fixing one colon issue

Git itself is shipped with summarization and visualization tools: the
\verb|git log| command and Gitk, which is a graphical tool for the
purpose of browsing the DAG of the repository. Many other tools are
designed with a similar visual metaphore as what is presented in Gitk,
including GitKraken, Github Desktop and web interfaces, the GitLab web
interface, the Bitbucket web interface, are a few examples. The Gitk
interface is built around the central DAG viewer. The DAG displays the
repository events on their respective branches, the author, and the date
that the event was authored. A user can select an event to view addition
information about it, including the full commit log, the parents and
children of the event, and the diff generated if modifications were
made. In the case of the Linux kernel, merges are not resolved as merge
conflicts in the master repository, but by the developers prior to
merging through rebase operations. With this development model, no
merges will have modified any files, and will not show a diff. While the
merge does not make changes directly, the effects of merging the commits
persist, but Gitk is unable to provide an aggregated view of the files
modified, the patches for those files, and the authors who contributed
commits to that merge.

>>>>

Git itself is shipped with summarization and visualization tools; Gitk
and \verb|git log --graph| are both built-in tools for the purpose of
visualizing and browsing the DAG of the repository. Many other tools are
designed with a similar visual metaphore as what is presented in Gitk,
including GitKraken, Github Desktop and web interfaces, the GitLab web
interface, the Bitbucket web interface, are a few examples. The Gitk
interface is built around the central DAG viewer. The DAG displays the
repository events on their respective branches, the author, and the date
that the event was authored. A user can select an event to view addition
information about it, including the full commit log, the parents and
children of the event, and the diff generated if modifications were
made. In the case of the Linux kernel, merges are not resolved as merge
conflicts in the master repository, but by the developers prior to
merging through rebase operations. With this development model, no
merges will have modified any files, and will not show a diff. While the
merge does not make changes directly, the effects of merging the commits
persist, but Gitk is unable to provide an aggregated view of the files
modified, the patches for those files, and the authors who contributed
commits to that merge.
